### 2018-07-06 paper/6-engineering.tex
Two minor rewordings

Deep constructive traces (\S\ref{sec-deep-constructive-traces}) combined with
task non-determinism (\S\ref{sec-non-determinism}) can lead to very subtle bugs,
especially in the cloud setting. Fig.~\ref{fig-frankenbuild} shows a
\emph{Frankenbuild}~\cite{esfahani2016cloudbuild} example, where the target
\cmd{report.txt}, which is downloaded from the cloud, is inconsistent with its
immediate dependency \cmd{main.prof}. This is caused by two factors:
(i)~inherent non-determinism of profiling: running a profiling tool on the very
same \cmd{main.exe} will produce different \cmd{main.prof} results every time;
and (ii)~relying on deep constructive traces, which cache build results based
only on the hashes of terminal task inputs (in this case \cmd{main.exe}). Note
that the resulting store is incorrect according to all three definitions of
correctness: the main definition (\S\ref{sec-build-correctness}), the variant
for non-deterministic tasks (\S\ref{sec-non-determinism}) and the variant for
shallow builds (this section).

>>>>

Deep constructive traces (\S\ref{sec-deep-constructive-traces}) combined with
task non-determinism (\S\ref{sec-non-determinism}) can lead to very subtle bugs,
especially in the cloud setting. Fig.~\ref{fig-frankenbuild} shows a
\emph{Frankenbuild}~\cite{esfahani2016cloudbuild} example, where the target
\cmd{report.txt}, which is downloaded from the cloud, is inconsistent with its
immediate dependency \cmd{main.prof}. This inconsistency is caused by two factors:
(i)~inherent non-determinism of profiling: running a profiling tool on the very
same \cmd{main.exe} will produce different \cmd{main.prof} results every time;
and (ii)~relying on deep constructive traces, which cache build results based
only on the hashes of terminal task inputs (in this case \cmd{main.exe}). Note
that the resulting store is incorrect according to all three definitions of
correctness: the main definition (\S\ref{sec-build-correctness}), the variant
for non-deterministic tasks (\S\ref{sec-non-determinism}) and the variant for
shallow builds (this section).
